Higher-Order unification for free!

### 2024-04-26 paper/main.tex
move description of proofs to end of section 2 since we need the idea of links to get it. Also make it short.

@@

When detailing examples, we represent links as equations between two
terms under a context.
The equality sign is subscripted with the
kind of \elpiIn{baselink}. For example $\linkbetaM{x}{A_x}{F_x~a}$ corresponds to:
\begin{elpicode}
abs x\ val (link-llam (uva A [x]) (app[uva F [x],con "a"]))
\end{elpicode}

>>>>

We prove \fullref{prop:fidelity} in
\cref{sec:eta,sec:beta,sec:invariant1}
and \fullref{prop:simulation} only in \cref{sec:llam},
where links are not present yet.
In order to prove \cref{prop:simulation} in the presence of links
one needs to refine \cref{prop:fidelity} by relating the two
substitutions: they are equivalent only by using decompilation to 
take into account terms in \linkStore.
Then, by induction
on the number of steps, \ref{prop:fidelity} implies \Cref{prop:simulation}.
We discuss \fullref{prop:fidelity-recovery} in \cref{sec:beta}.

@@

In the examples we represent links as equations
%between two terms
under a context.
The equality sign is subscripted with the
kind of \elpiIn{baselink}. For example $\linkbetaM{x}{A_x}{F_x~a}$ corresponds to:
\begin{elpicode}
abs x\ val (link-llam (uva A [x]) (app[uva F [x],con "a"]))
\end{elpicode}
